---
title: "R Notebook"
output: html_notebook
runtime: shiny
---

Here we will start looking at choropleths...

#Materials template is from- https://www.r-bloggers.com/first-step-on-gis-with-r/.  

##Load Packages
```{r}
library(maptools)
library(rgdal)     # R wrapper around GDAL/OGR
library(rgeos)
library(ggplot2)   # for general plotting
library(ggmap)     # for fortifying shapefiles
library(dplyr)
```

##Load Data
```{r}
#Map of Indonesia
provIndo <- 
    readShapeSpatial("/Users/User/Desktop/UNICEF/Maps/shape/IDN_adm1.shp")

#SDG Data
df = read.csv(file = "/Users/User/Desktop/UNICEF/SDG Datasheet for Dashboard Development v2.csv", sep=",")
SDG = df[,colSums(is.na(df)) != nrow(df)]
```

##Plot map to make sure its working using base plot
```{r}
plot(provIndo)
```

##Range of map
```{r}
provIndo@bbox
```

#Materials from https://gist.github.com/lmullen/8375785

More data modification

```{r}
# Next the shapefile has to be converted to a dataframe for use in ggplot2
shapefile_df <- fortify(provIndo)

#ID to province
idNum <- shapefile_df %>% 
        mutate(Province = ifelse(id==0, "Aceh", ifelse(id==1, "Bali", ifelse(id==3, "Banten", ifelse(id==4, "Bengkulu", ifelse(id==33, "DI Yogyakarta", ifelse(id==7, "DKI Jakarta", ifelse(id==5, "Gorontalo", ifelse(id==8, "Jambi", ifelse(id==9, "Jawa Barat", ifelse(id==10, "Jawa Tengah", ifelse(id==11, "Jawa Timur", ifelse(id==12, "Kalimantan Barat", ifelse(id==13, "Kalimantan Selatan", ifelse(id==14, "Kalimantan Tengah", ifelse(id==15, "Kalimantan Timur", ifelse(id==16, "Kalimantan Utara", ifelse(id==2, "Kepulauan Bangka Belitung", ifelse(id==17, "Kepulauan Riau", ifelse(id==18, "Lampung", ifelse(id==20, "Maluku", ifelse(id==19, "Maluku Utara", ifelse(id==21, "Nusa Tenggara Barat", ifelse(id==22, "Nusa Tenggara Timur", ifelse(id==23, "Papua", ifelse(id==6, "Papua Barat", ifelse(id==24, "Riau", ifelse(id==25, "Sulawesi Barat", ifelse(id==26, "Sulawesi Selatan", ifelse(id==27, "Sulawesi Tengah", ifelse(id==28, "Sulawesi Tenggara", ifelse(id==29, "Sulawesi Utara", ifelse(id==30, "Sumatera Barat", ifelse(id==31, "Sumatera Selatan", "Sumatera Utara"))))))))))))))))))))))))))))))))))
```

Now the shapefile can be plotted as either a geom_path or a geom_polygon. Paths handle clipping better. Polygons can be filled. You need the aesthetics long, lat, and group.

```{r}
map <- ggplot() +
geom_path(data = shapefile_df, 
          aes(x = long, y = lat, group = group),
          color = 'gray', fill = 'white', size = .2)

print(map) 
```

Using the ggplot2 function coord_map will make things look better and it will also let you change the projection. But sometimes with large shapefiles it makes everything blow up.

```{r}
map_projected <- map +
  coord_map()
  
print(map_projected)
```

From- http://eriqande.github.io/rep-res-web/lectures/making-maps-with-R.html

```{r}
ggplot(data = shapefile_df) + 
  geom_polygon(aes(x = long, y = lat, fill = id, group = group), color = "white") + 
  coord_fixed(1.3) +
  guides(fill=FALSE)  # do this to leave off the color legend
```


From- http://eriqande.github.io/rep-res-web/lectures/making-maps-with-R.html

```{r}
ggplot(data = idNum) + 
  geom_polygon(aes(x = long, y = lat, fill = id, group = group), color = "white") + 
  coord_fixed(1.3) +
  guides(fill=FALSE)  # do this to leave off the color legend
```

quantiles from- https://timogrossenbacher.ch/2016/12/beautiful-thematic-maps-with-ggplot2-only/#a-better-color-scale

```{r}
SDG1 <- SDGdf %>%
  filter(Indicator == "Proportion of population living below the national poverty line", Level == "Provincial")

cacopa <- inner_join(idNum, SDG1, by = "Province")

cacopa$Value <- as.numeric(as.character(cacopa$Value))

# Number of color levels
no_classes <- 4

quantiles <- quantile(cacopa$Value, 
                      probs = seq(0, 1, length.out = no_classes + 1))

# here I define custom labels (the default ones would be ugly)
labels <- c()
for(idx in 1:length(quantiles)){
  labels <- c(labels, paste0(round(quantiles[idx], 2), 
                             " - ", 
                             round(quantiles[idx + 1], 2)))
}
# I need to remove the last label 
# because that would be something like "66.62 - NA"
labels <- labels[1:length(labels)-1]

# here I actually create a new 
# variable on the dataset with the quantiles
cacopa$Value_quantiles <- cut(cacopa$Value, 
                                     breaks = quantiles, 
                                     labels = labels, 
                                     include.lowest = T)
```

https://timogrossenbacher.ch/2016/12/beautiful-thematic-maps-with-ggplot2-only/#a-better-color-scale

```{r}
p <- ggplot() +
    # municipality polygons (watch how I 
   # use the new variable for the fill aesthetic)
    geom_polygon(data = cacopa, aes(fill = Value_quantiles, 
                                      x = long, 
                                      y = lat, 
                                      group = group)) +
    # municipality outline
    geom_path(data = cacopa, aes(x = long, 
                                   y = lat, 
                                   group = group), 
              color = "white", size = 0.1) +
    coord_equal() +
    theme_map() +
    labs(x = NULL, 
         y = NULL, 
         title = "Goal 1: No Poverty", 
         subtitle = "Proportion of population living below the national poverty line", 
         caption = "SDG Baseline Report on children in Indonesia") +
  # now the discrete-option is used, 
  # and we use guide_legend instead of guide_colourbar
  scale_fill_viridis(
    option = "viridis",
    name = "Value",
    discrete = T,
    direction = -1,
    guide = guide_legend(
     keyheight = unit(5, units = "mm"),
     title.position = 'top',
     reverse = T
  ))
p
```



```{r}
shapefileBase <- ggplot(data = shapefile_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "white", fill = "gray")
shapefileBase #+ theme_nothing()
```


```{r}
ditch_the_axes <- theme(
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  panel.border = element_blank(),
  panel.grid = element_blank(),
  axis.title = element_blank()
  )

elbow_room1 <- shapefileBase + 
      geom_polygon(data = cacopa, aes(fill = Value), color = "white") +
      geom_polygon(color = "white", fill = NA) +
      theme_bw() +
      ditch_the_axes

elbow_room1 + scale_fill_gradientn(na.value = "grey", colours = c("deepskyblue3", "orange3","red4", "chocolate4"))

elbow_room1 = theme(text = element_text(family = "Arial Narrow", size = 8),
          plot.title = element_text(size = 12, face = "bold"),
          plot.margin = unit(c(0, 0.25, 0.0, 0.25), "in"),
          panel.border = element_rect(fill = NA, colour = "#cccccc"),
          legend.text = element_text(size = 8),
          legend.position = c(0.9, 0.25))
```

