---
title: "Dynamic Tables"
author: "Millie"
date: "11 September 2017"
output: html_notebook
runtime: shiny
---

###Packages

```{r LoadPackages}
library(shiny)
library(DT)
library(ggplot2)
library(dplyr)
```

###Data

```{r LoadData}
#SDG Data
df = read.csv(file = "/Users/User/Desktop/R Prac/UNICEF Project/SDG.csv", sep=",")

#Remove empty columns from dataset 
SDG = df[,colSums(is.na(df)) != nrow(df)]

SDGdf1 <- SDG[1:4112,] %>%
        mutate(Level = ifelse(Province == "All Indonesia", "National", 
                              "Provincial"))


SDGdf <- SDGdf1 %>%
        select("SDG" = "SDG.Goal", "Indicator" = "Indicator", "Value" = "Value", "Level" = "Level", "Province" = "Province",  "Gender" = "Gender..All.Male.Female.", "Geography" = "Geography..All.Urban.Rural.", "Disability" = "Disability..All.With.Without.", "WealthQuantile" = "Wealth.Quintile..All.Poorest.Second.Middle.Fourth.Richest.", "Education" = "Educational.attainment.of.household.head", "Age" = "Age.Range..i.e..0.24.M..15.60.Y.", "Year" = "Year", "Source" = "Source")

SDGnames <- c("Goal 1: No Poverty", "Goal 2: Zero Hunger", "Goal 3: Good Health and Well-Being", "Goal 4 : Quality Education", "Goal 5: Gender Equality", "Goal 6: Clean Water and Sanitation", "Goal 8: Decent Work and Economic Growth", "Goal 13: Climate Action", "Goal 16: Peace Justice and Strong Institutions") 

SDGs <- c("Goal 1: No Poverty" = 1, "Goal 2: Zero Hunger" = 2, "Goal 3: Good Health and Well-Being" = 3, "Goal 4 : Quality Education" = 4, "Goal 5: Gender Equality" = 5, "Goal 6: Clean Water and Sanitation" = 6, "Goal 8: Decent Work and Economic Growth" = 8, "Goal 13: Climate Action" = 13, "Goal 16: Peace Justice and Strong Institutions" = 16)

```

##Easy Example 



##Example 1

Basic dynamic table from https://shiny.rstudio.com/articles/datatables.html

```{r Example1}
ui <- basicPage(
  h2("SDG Data"),
  DT::dataTableOutput("mytable")
)

server <- function(input, output) {
  output$mytable = DT::renderDataTable({
    SDGdf
  })
}
  
shinyApp(ui, server)
```


##Example 2

Large dynamic table from https://shiny.rstudio.com/articles/datatables.html

```{r Example2}
ui <- fluidPage(
  title = "Examples of DataTables",
  sidebarLayout(
    sidebarPanel(
      conditionalPanel(
        'input.dataset === "diamonds"',
        checkboxGroupInput("show_vars", "Columns in diamonds to show:",
                           names(diamonds), selected = names(diamonds))
      ),
      conditionalPanel(
        'input.dataset === "mtcars"',
        helpText("Click the column header to sort a column.")
      ),
      conditionalPanel(
        'input.dataset === "iris"',
        helpText("Display 5 records by default.")
      )
    ),
    mainPanel(
      tabsetPanel(
        id = 'dataset',
        tabPanel("diamonds", DT::dataTableOutput("mytable1")),
        tabPanel("mtcars", DT::dataTableOutput("mytable2")),
        tabPanel("iris", DT::dataTableOutput("mytable3"))
      )
    )
  )
)

server <- function(input, output) {
  
  # choose columns to display
  diamonds2 = diamonds[sample(nrow(diamonds), 1000), ]
  output$mytable1 <- DT::renderDataTable({
    DT::datatable(diamonds2[, input$show_vars, drop = FALSE])
  })
  
  # sorted columns are colored now because CSS are attached to them
  output$mytable2 <- DT::renderDataTable({
    DT::datatable(mtcars, options = list(orderClasses = TRUE))
  })
  
  # customize the length drop-down menu; display 5 rows per page by default
  output$mytable3 <- DT::renderDataTable({
    DT::datatable(iris, options = list(lengthMenu = c(5, 30, 50), pageLength = 5))
  })
  
}

shinyApp(ui, server)
```

##Check box group example

From- https://shiny.rstudio.com/reference/shiny/latest/checkboxGroupInput.html

```{r CheckboxExample}
ui <- fluidPage(
  checkboxGroupInput("variable", "Variables to show:",
                     c("Cylinders" = "cyl",
                       "Transmission" = "am",
                       "Gears" = "gear")),
  tableOutput("data")
)

server <- function(input, output, session) {
  output$data <- renderTable({
    mtcars[, c("mpg", input$variable), drop = FALSE]
  }, rownames = TRUE)
}

shinyApp(ui, server)
```

##Icon Example

```{r IconExample}
ui <- fluidPage(
  checkboxGroupInput("icons", "Choose icons:",
    choiceNames =
      list(icon("calendar"), icon("bed"),
           icon("cog"), icon("bug")),
    choiceValues =
      list("calendar", "bed", "cog", "bug")
  ),
  textOutput("txt")
)

server <- function(input, output) {
  output$txt <- renderText({
    icons <- paste(input$icons, collapse = ", ")
    paste("You chose", icons)
  })
}

shinyApp(ui, server)
```

##Downloadable Table

Script from- https://shiny.rstudio.com/articles/download.html

##Interactive table and figure using DT

Script from- https://rstudio.github.io/DT/shiny.html 

###Example 1

```{r ColorCells}
DT::renderDataTable({
  datatable(SDGdf) %>% formatStyle(
    'Province',
    backgroundColor = styleInterval(3.4, c('gray', 'yellow'))
  )
})
```


###Final Example Interactive Table and Plot

Dynamic table from https://shiny.rstudio.com/articles/datatables.html

```{r ReactiveTableAndPlot}
ui <- fluidPage(

  title = 'Select Table Rows',

  h1('A Client-side Table'),

  fluidRow(
    column(6, DT::dataTableOutput('x1')),
    column(6, plotOutput('x2', height = 500))
  ),

  hr(),

  h1('A Server-side Table'),

  fluidRow(
    column(9, DT::dataTableOutput('x3')),
    column(3, verbatimTextOutput('x4'))
  )

)

server <- function(input, output){

  output$x1 = DT::renderDataTable(cars, server = FALSE)

  # highlight selected rows in the scatterplot
  output$x2 = renderPlot({
    s = input$x1_rows_selected
    par(mar = c(4, 4, 1, .1))
    plot(cars)
    if (length(s)) points(cars[s, , drop = FALSE], pch = 19, cex = 2)
  })

  # server-side processing
  mtcars2 = mtcars[, 1:8]
  output$x3 = DT::renderDataTable(mtcars2, server = TRUE)

  # print the selected indices
  output$x4 = renderPrint({
    s = input$x3_rows_selected
    if (length(s)) {
      cat('These rows were selected:\n\n')
      cat(s, sep = ', ')
    }
  })

}
shinyApp(ui, server)
```

###Notes

Pre-selection

The selection argument of datatable() can also include a component selected to specify which rows/columns/cells to be pre-selected when the table is initialized. When target = 'row' or 'column', selected is a vector of row or column indices. For the case of target = 'row+column', selected should be a list of two components rows and cols, e.g. list(rows = c(1, 2, 4, 9), cols = c(1, 3)). For target = 'cell', it should be a matrix of two columns: the first column is the row indices of selected cells, and the second column is the column indices.

##Mine

The data

```{r SelectSDG1}
SDG1 <- SDGdf%>%
        filter(SDG==1)
```

##Minimum working example

Dynamic table from https://shiny.rstudio.com/articles/datatables.html

```{r MyData}
ui <- fluidPage(
  titlePanel("Sustainable Development Goals"),
  sidebarLayout(
    sidebarPanel(
      checkboxGroupInput(inputId = "show_vars", label = "Columns for Goal 1: No Poverty",
                           choices = names(SDG1), selected = names(SDG1)
      ),
      # Button
      downloadButton("downloadData", "Download")    
      ),

    mainPanel(
      tabsetPanel(
        id = 'dataset',
        tabPanel("SDG1", DT::dataTableOutput("SDGtable1")))
      )
    )

  )


server <- function(input, output) {
  
        SDG1 <- SDGdf%>%
        filter(SDG==1)
        
  # choose columns to display
  output$SDGtable1 <- DT::renderDataTable({
    DT::datatable(SDG1[, input$show_vars, drop = FALSE])
  })
  
   # Downloadable csv of selected dataset ----
  output$downloadData <- downloadHandler(
    filename = function() {
      paste(input$dataset, ".csv", sep = "")
    },
    content = function(file) {
      write.csv(datasetInput(), file, row.names = FALSE)
    })
}

shinyApp(ui, server)
```

Making 3 tabs 

Large dynamic table from https://shiny.rstudio.com/articles/datatables.html

**Cannot get the checkboxgroup to work....**

```{r MyDataTabs}
#Generate Data
SDG1 <- SDGdf%>%
        filter(SDG==1)
        
SDG2 <- SDGdf%>%
        filter(SDG==2)
        
SDG3 <- SDGdf%>%
        filter(SDG==3)

#Generate tables
ui <- fluidPage(
  titlePanel("Sustainable Development Goals"),
  sidebarLayout(
    sidebarPanel(
      conditionalPanel (
        condition = 'input.dataset === "SDG1"',
        checkboxGroupInput(inputId = "show_vars1", label = "Columns for Goal 1: No Poverty",
                           choices = names(SDG1), selected = names(SDG1))
      ),
      conditionalPanel(
        'input.dataset === "SDG2"',
        checkboxGroupInput(inputId = "show_vars2", label = "Columns for Goal 2: Zero Hunger",
                           choices = names(SDG2), selected = names(SDG2))
      ),
      conditionalPanel(
        'input.dataset === "SDG3"',
        checkboxGroupInput(inputId = "show_vars3", label = "Columns for Goal 3: Good Health and Well-Being",
                           choices = names(SDG3), selected = names(SDG3))
      ),
        # Button
      downloadButton("downloadData", "Download")
    ),
   mainPanel(
      tabsetPanel(
        id = 'dataset',
        tabPanel("SDG 1", DT::dataTableOutput("SDGtable1")),
        tabPanel("SDG 2", DT::dataTableOutput("SDGtable2")),
        tabPanel("SDG 3", DT::dataTableOutput("SDGtable3"))
        )
      )
  )
)


server <- function(input, output) {

        output$SDGtable1 <- DT::renderDataTable({
                DT::datatable(SDG1[, input$show_vars1, drop = FALSE])
                })
        
        output$SDGtable2 <- DT::renderDataTable({
                DT::datatable(SDG2[, input$show_vars2, drop = FALSE])
                })
        
        output$SDGtable3 <- DT::renderDataTable({
                DT::datatable(SDG3[, input$show_vars3, drop = FALSE])
                })  
       
        # Downloadable csv of selected dataset ----
        output$downloadData <- downloadHandler(
                filename = function() {
                        paste(input$dataset, ".csv", sep = "")
                        },
                content = function(file) {
                        write.csv(datasetInput(), file, row.names = FALSE)
                })
        }

shinyApp(ui, server)
```

### Playing with interactive table + graph

NEEDS WORK!!! 

```{r MyDataInteractiveGraph}
ui <- fluidPage(

  title = 'Select Table Rows',

  h1('A Client-side Table'),

  fluidRow(
    column(6, DT::dataTableOutput('x1')),
    column(6, plotOutput('x2', height = 500))
  ),

  hr(),

  h1('A Server-side Table'),

  fluidRow(
    column(9, DT::dataTableOutput('x3')),
    column(3, verbatimTextOutput('x4'))
  )

)

server <- function(input, output){

  output$x1 = DT::renderDataTable(SDGdf, server = FALSE)

  # highlight selected rows in the scatterplot
  output$x2 = renderPlot({
    s = input$x1_rows_selected
    par(mar = c(4, 4, 1, .1))
    plot(SDGdf)
    if (length(s)) points(SDGdf[s, , drop = FALSE], pch = 19, cex = 2)
  })

  # server-side processing
  SDGdf2 = SDGdf[, 1:8]
  output$x3 = DT::renderDataTable(SDGdf2, server = TRUE)

  # print the selected indices
  output$x4 = renderPrint({
    s = input$x3_rows_selected
    if (length(s)) {
      cat('These rows were selected:\n\n')
      cat(s, sep = ', ')
    }
  })

}
shinyApp(ui, server)
```

## Download with drop down to select data- works for my data

Code from- https://shiny.rstudio.com/articles/download.html

```{r MyDataWithDropdown}
ui <- fluidPage(

  # App title ----
  titlePanel("Downloading Data"),

  # Sidebar layout with input and output definitions ----
  sidebarLayout(

    # Sidebar panel for inputs ----
    sidebarPanel(

      # Input: Choose dataset ----
      selectInput("dataset", "Choose a Sustainable Development Goal:",
                  choices = c("Goal 1: No Poverty", "Goal 2: Zero Hunger", "Goal 3: Good Health and Well-Being", "Goal 4 : Quality Education", "Goal 5: Gender Equality", "Goal 6: Clean Water and Sanitation", "Goal 8: Decent Work and Economic Growth", "Goal 13: Climate Action", "Goal 16: Peace Justice and Strong Institutions")),

      # Button
      downloadButton("downloadData", "Download")

    ),

    # Main panel for displaying outputs ----
    mainPanel(

      tableOutput("table")

    )

  )
)

server <- function(input, output) {

        #Generate Data
SDG1 <- SDGdf%>%
        filter(SDG==1)
        
SDG2 <- SDGdf%>%
        filter(SDG==2)
        
SDG3 <- SDGdf%>%
        filter(SDG==3)

SDG4 <- SDGdf%>%
        filter(SDG==4)

SDG5 <- SDGdf%>%
        filter(SDG==5)

SDG6 <- SDGdf%>%
        filter(SDG==6)

SDG8 <- SDGdf%>%
        filter(SDG==8)

SDG13 <- SDGdf%>%
        filter(SDG==13)

SDG16 <- SDGdf%>%
        filter(SDG==16)
        
  # Reactive value for selected dataset ----
  datasetInput <- reactive({
    switch(input$dataset,
           "Goal 1: No Poverty" = SDG1, "Goal 2: Zero Hunger" = SDG2, "Goal 3: Good Health and Well-Being" = SDG3, "Goal 4 : Quality Education" = SDG4, "Goal 5: Gender Equality" = SDG5, "Goal 6: Clean Water and Sanitation" = SDG6, "Goal 8: Decent Work and Economic Growth" = SDG8, "Goal 13: Climate Action" = SDG13, "Goal 16: Peace Justice and Strong Institutions" = SDG16
)
  })

  # Table of selected dataset ----
  output$table <- renderTable({
    datasetInput()
  })

  # Downloadable csv of selected dataset ----
  output$downloadData <- downloadHandler(
    filename = function() {
      paste(input$dataset, ".csv", sep = "")
    },
    content = function(file) {
      write.csv(datasetInput(), file, row.names = FALSE)
    }
  )

}
shinyApp(ui, server)
```

## Final dynamic table- dropdown and checkbox, working for my data

https://stackoverflow.com/questions/45460304/making-a-dynamic-checkboxgroupinput-with-shiny

```{r MyDataWithDropdownAndCheckbox}
  ui <- fluidPage(
    # App title ----
  titlePanel("Downloading Data"),

  # Sidebar layout with input and output definitions ----
  sidebarLayout(

    # Sidebar panel for inputs ----
    sidebarPanel(
            # SDG Input
            selectInput("select1", "Select SDG:", choices = c(
"Goal 1: No Poverty" = 1, "Goal 2: Zero Hunger" = 2, "Goal 3: Good Health and Well-Being" = 3, "Goal 4 : Quality Education" = 4, "Goal 5: Gender Equality" = 5, "Goal 6: Clean Water and Sanitation" = 6, "Goal 8: Decent Work and Economic Growth" = 8, "Goal 13: Climate Action" = 13, "Goal 16: Peace Justice and Strong Institutions" = 16), selected = "Goal 1: No Poverty"),

            #Checkbox output 
            uiOutput("checkbox"),

            # Button
            downloadButton("downloadData", "Download")
    ),

    # Main panel for displaying outputs ----
    mainPanel(
            # Table output
            DT::dataTableOutput("SDGtable1")
    )
  )
)

  # Server function
  server <- function(input, output){
          
          # Generate the checkbox
          output$checkbox <- renderUI({
                  choice <-  unique(SDGdf[SDGdf$SDG %in% input$select1, "Indicator"])
                  checkboxGroupInput("checkbox","Select Indicator", choices = choice, selected = choice[1])
                  })
          
          # Generate data frame
          df <-reactive({
                  SDGdf %>% 
                          filter(SDGdf$SDG %in% input$select1, SDG$Indicator %in% input$checkbox)
                  })
          
          # Generate data table 
          output$SDGtable1 <- DT::renderDataTable({
                  DT::datatable(df())
                  })
          
          # Downloadable csv of selected dataset ----
          output$downloadData <- downloadHandler(
                filename = function() {
                        paste(input$dataset, ".csv", sep = "")
                        },
                content = function(file) {
                        write.csv(datasetInput(), file, row.names = FALSE)
                })
     
   }
shinyApp(ui, server)
```


## Final dynamic table- dropdown and checkbox, working for my data

https://stackoverflow.com/questions/45460304/making-a-dynamic-checkboxgroupinput-with-shiny

```{r MyDataWithDropdownAndCheckboxAndLevelCheckbox}
SDGdf2 <- SDGdf %>%
        filter(Province == "Aceh")

SDGprov <- SDGdf2%>%
        select("SDG", "Indicator" = "Indicator", "Value" = "Value", "Province" = "Province", "Age" = "Age", "Year" = "Year", "Source" = "Source")



ui <- fluidPage(
    # App title ----
  titlePanel("Downloading Data"),

  # Sidebar layout with input and output definitions ----
  sidebarLayout(

    # Sidebar panel for inputs ----
    sidebarPanel(
            # SDG Input
            selectInput("select1", "Select Sustainable Development Goal:", choices = c(
"Goal 1: No Poverty" = 1, "Goal 2: Zero Hunger" = 2, "Goal 3: Good Health and Well-Being" = 3, "Goal 4 : Quality Education" = 4, "Goal 5: Gender Equality" = 5, "Goal 6: Clean Water and Sanitation" = 6, "Goal 8: Decent Work and Economic Growth" = 8, "Goal 13: Climate Action" = 13, "Goal 16: Peace Justice and Strong Institutions" = 16), selected = "Goal 1: No Poverty"),

            #Checkbox output 
            uiOutput("checkbox1"),

            # Button
            downloadButton("downloadData", "Download")
    ),

    # Main panel for displaying outputs ----
    mainPanel(
            
            #Checkbox output 
            #uiOutput("checkbox2"),
            
            # Table output
            DT::dataTableOutput("SDGtable1")
    )
  )
)

  # Server function
  server <- function(input, output){
          
          # Generate the checkbox
          output$checkbox1 <- renderUI({
                  choice <-  unique(SDGprov[SDGprov$SDG %in% input$select1, "Indicator"])
                  checkboxGroupInput("checkbox1","Select Indicator:", choices = choice, 
                                     selected = choice[1])
                  })
          
          # Generate the checkbox
          #output$checkbox2 <- renderUI({
           #       choiceLevel <-  unique(SDGprov[SDGprov$Indicator %in% input$checkbox1, "Level"])
            #      checkboxGroupInput("checkbox2","Select Level:", choices = choiceLevel,
             #                        selected = choiceLevel[1])
              #    })
          
          # Generate data frame
          df <-reactive({
                  SDGprov %>% 
                          filter(SDGprov$SDG %in% input$select1, 
                                 SDGprov$Indicator %in% input$checkbox1#,
                                 #SDGprov$Level %in% input$checkbox2
                                 )
   
                  })
          
          # Generate data table 
          output$SDGtable1 <- DT::renderDataTable({
                  DT::datatable(df())
                  })
          
          # Downloadable csv of selected dataset ----
          output$downloadData <- downloadHandler(
                filename = function() {
                        paste(input$dataset, ".csv", sep = "")
                        },
                content = function(file) {
                        write.csv(datasetInput(), file, row.names = FALSE)
                })
     
   }
shinyApp(ui, server)
```

## Dynamic table with column head dropdowns  

Code from- https://stackoverflow.com/questions/33797072/r-datatable-hide-search-box-for-individual-columns

```{r TableWithColumnDropdowns}
 ui = fluidPage(tags$head(tags$style(
    HTML("input[type='search']:disabled {visibility:hidden}")
  )),
  titlePanel("Downloading Data"),

  # Sidebar layout with input and output definitions ----
  sidebarLayout(

    # Sidebar panel for inputs ----
    sidebarPanel(
            # SDG Input
            checkboxGroupInput("show_vars", "Desired Data to Display:",
                           names(SDGdf), selected = names(SDGdf))
            ),

            # Button
            downloadButton("downloadData", "Download")
    ),

    # Main panel for displaying outputs ----
    mainPanel(
            # Table output
            DT::dataTableOutput("tbl")
    )
  )

  server = function(input, output) {
          
    output$tbl = DT::renderDataTable(datatable(
      SDGdf[, input$show_vars, drop = FALSE],
      filter = 'top',
      options = list(columnDefs = list(list(
        targets = c("SDG", "Indicator", "Level", "Gender"), searchable = FALSE
      )),
      pageLength = 10)
    ))
  }

shinyApp(ui, server)
```

